HO unification from object language to meta language

### 2024-03-27 paper/main.tex
eta add some def

>>>>

Compiling term with \maybeeta terms forces us to determine if, $\lambda x. T_x$,
for any term $T$ having $x$ in scope, can be a $\eta$-expansion, i.e. under a
given substitution $\sigma$, we have $\sigma (\lambda x.T_x) = t$. This
\maybeeta detection is not a trivial operation as it may seems.
%
\begin{gather}
  \lambda x. f \appsep A_x\\
  \lambda x. f \appsep x \appsep A_x\\
  \lambda x. \lambda y. f \appsep A_x \appsep B_{y x}\\ \label{eq:lamlam}
\end{gather}

In the examples above, the first expression is a \maybeeta since $A_x$ can
reduce to $x$, the second one is not a \maybeeta since for any substitution for
$A_x$, $x$ is not free in $f \appsep x$. The third equation is a bit more
complicated since, we have a vector of lambdas, this means that the whole term
is a \maybeeta, if the inner $\lambda$-term is an $\eta$-expansion of a term
$t$, and $t$ can be reduced to a term on the form $t' x$ where $x$ is not free
in $t'$. Indeed, eq.~\ref{eq:lamlam} is a \maybeeta under the substitution 
$\sigma = \{A \mapsto \lambda x.x, B \mapsto \lambda x. \lambda y. x\}$.

As a remark, note that $\lambda x. f \appsep A_x \appsep x$ is a \maybeeta,
since, despite, $x$ occurs in $f \appsep A_x$, it is still possible that this
subterm does not use $x$, for example if $A$ is a function on the form $\lambda
x.a$, where $a$ is a defined constant. In this case, the \maybeeta should
consider that the bound variable \elpiIn{x} does not ``rigidly'' occur in 
the given subterm.

We can now define more formally the two auxiliary relation we need for \maybeeta
detection:

\begin{definition}[reduce-to]
  For any term $t$, $\lambda x_1 \ldots x_n.t_{x_0\ldots x_n}$ reduces to a bound
  variable $x$ if one of the three following cases is satisfied: 1)
  $n = 0$ and $t = x$; 2) $t$ is the application of $x$ to a list
  of term $l$ and each $l_i$ reduces to $x_i$; 3) $t$ is a variable with scope
  $s$, and for any $bv \in [x|\vec{x}]$, it exists a $s_i$, such that $s_i$
  reduces to $bv$
\end{definition}

\begin{definition}[occurs-rigidly]
  Given a term $t$, a bund variable ``rigidly'' occurs in \subterm{t} this
  term does not appear in the scope of a variable
\end{definition}

TODO: maybe eta is over-approximation
